Fifteen years of decentralization attempts

### 2014-03-21 paper.tex
Add I2P to conclusion (lot of checkmarks)

	In the last section, we discussed existing decentralized peer-to-peer networks. In this section we will make a comparison between these networks. For each network, we will explain the following features:

@@

	\begin{landscape}
		\begin{table}[p]
			\include{table}
		\end{table}
	\end{landscape}

@@

	From the decentralization table, we come to the conclusion that there is no complete decentralized system that provides the full functionality and security that Tor offers today. While a lot of research has been done on decentralized systems, there is no system yet that can compete with Tor. Decentralized systems that do exist such as Tarzan, Torsk or Gnutella, show promising attempts to decentralize and anonymize the internet. Yet each of these systems either lacks in performance or is vulnerable to some type of attack.

>>>>

	In the last section, we discussed existing decentralized peer-to-peer networks. In this section we will make a comparison between these networks, as seen in table \ref{tbl:comparison}. For each network, we will explain the following features:

@@

	\begin{landscape}
		\begin{table}[p]
			\centering
			\include{table}
			\caption{A comparison of decentralized peer-to-peer overlay networks}
			\label{tbl:comparison}
		\end{table}
	\end{landscape}

@@

	From the decentralization table, we come to the conclusion that there is no complete decentralized system that provides the full functionality and security that Tor offers today. While a lot of research has been done on decentralized systems, there is no system yet that can compete with Tor. Decentralized systems that do exist such as Tarzan, I2P, Torsk or Gnutella, show promising attempts to decentralize and anonymize the internet. Yet each of these systems either lacks in performance or is vulnerable to some type of attack.

### 2014-03-21 table.tex
Replaced a bunch of question marks in the table, still a few left

\begin{center}
    \begin{longtable}{ | p{1.9cm} | p{0.8cm} | p{2.5cm} | p{2.5cm} | p{2.5cm} | p{2.5cm} | p{2.5cm} | p{2.5cm} | p{2.5cm} | }
  		\caption{A comparison of decentralized peer-to-peer overlay networks} \\ \hline
	    \textbf{Name} & \textbf{Year} & \textbf{Tor interoperability} & \textbf{Public implementation} & \textbf{Used in practice} & \textbf{(D)DoS protection} & \textbf{Sybil attack protection} & \textbf{MITM protection} & \textbf{Provides anonymity} \\ \hline
		\endfirsthead

		Gnutella & 2000 & \xmark & \checkmark & \checkmark & \xmark & \xmark & \xmark & \xmark \\ \hline
		Freenet & 2001 & \xmark & \checkmark & \checkmark & \checkmark & \xmark & \xmark & \checkmark \\ \hline
		Tapestry & 2001 & \xmark & \checkmark & \checkmark & \checkmark & \xmark & \xmark & \xmark \\ \hline
		Pastry & 2001 & \xmark & \checkmark & \checkmark & \checkmark & \xmark & \xmark & \xmark \\ \hline
		AP3 & 2004 & \xmark & \xmark & \xmark & ? & ? & ? & \checkmark \\ \hline
		Tarzan & 2002 & \xmark & \xmark & \xmark & ? & ? & ? & \checkmark \\ \hline
		MorphMix & 2002 & \xmark & \checkmark & ? & ? & ? & ? & \checkmark \\ \hline
		I2P & 2003 & \xmark & \checkmark & \checkmark & ? & ? & ? & \checkmark\\ \hline
		Salsa & 2006 & \xmark & ? & ? & ? & ? & ? & ?\\ \hline
		Tribler & 2008 & \xmark & \checkmark & \checkmark & ? & ? & ? & \xmark \\ \hline
		Torks & 2009 & \checkmark & \xmark & \xmark & ? & ? & ? & \checkmark \\ \hline
		NISAN & 2009 & \xmark & \xmark & \xmark & ? & ? & ? & \checkmark \\ \hline
    \end{longtable}
\end{center}

>>>>

\begin{tabular}[p]{| l | l | p{2.5cm} | p{2.5cm} | p{2.5cm} | p{2.5cm} | p{2.5cm} | p{2.5cm} | p{2.5cm} |}
	\hline
	\textbf{Name} & \textbf{Year} & \textbf{Tor interoperability} & \textbf{Public implementation} & \textbf{Used in \newline practice} & \textbf{(D)DoS protection} & \textbf{Sybil attack protection} & \textbf{MITM \newline protection} & \textbf{Provides \newline anonymity} \\ \hline

	Gnutella & 2000 & \xmark & \checkmark & \checkmark & \xmark & \xmark & \xmark & \xmark \\ \hline
	Freenet & 2001 & \xmark & \checkmark & \checkmark & \checkmark & \xmark & \xmark & \checkmark \\ \hline
	Tapestry & 2001 & \xmark & \checkmark & \checkmark & \checkmark & \xmark & \xmark & \xmark \\ \hline
	Pastry & 2001 & \xmark & \checkmark & \checkmark & \checkmark & \xmark & \xmark & \xmark \\ \hline
	AP3 & 2004 & \xmark & \xmark & \xmark & ? & ? & ? & \checkmark \\ \hline
	Tarzan & 2002 & \xmark & \xmark & \xmark & ? & \checkmark & ? & \checkmark \\ \hline
	MorphMix & 2002 & \xmark & \checkmark & \xmark & \checkmark & \xmark & ? & \checkmark \\ \hline
	I2P & 2003 & \xmark & \checkmark & \checkmark & \checkmark & \checkmark & ? & \checkmark\\ \hline
	Salsa & 2006 & \xmark & \xmark & \xmark & \checkmark & \checkmark & ? & \checkmark \\ \hline
	Tribler & 2008 & \xmark & \checkmark & \checkmark & \checkmark & \xmark & \xmark & \xmark \\ \hline
	Torsk & 2009 & \checkmark & \xmark & \xmark & \checkmark & \checkmark & \checkmark & \checkmark \\ \hline
	NISAN & 2009 & \xmark & \xmark & \xmark & ? & ? & \checkmark & \checkmark \\ \hline		
\end{tabular}
